---
title: "heart_disease"
author: "David Baptista"
date: "2025-07-10"
output: html_document
---

WARNING: computations were made using a HAL server. Local machine is only useful if smaller experiments are made or for your personal use
```{r Loading the Package}
# -----------------------------------------
# Local Machine (directly from GitHub)
# -----------------------------------------
#remove.packages ("BAS", source = "CRAN")
#devtools::install_github (
#  "davidembb20/BAS",
#  ref = "costs_and_factors",
#  force = TRUE
#)
# -----------------------------------------
# HAL server
# -----------------------------------------
# e.g., download the package from GitHub to your local machine and then to the server, and set that folder as wd
#install.packages (".", repos = NULL, type = "source")
# -----------------------------------------

Sys.setenv(OMP_NUM_THREADS = "1", OPENBLAS_NUM_THREADS = "1") # Faster parallel computing
# to use with multisession, deliberately (not multicore), so that workers don´t end up fighting over cores.
library (BAS)
```

# Heart Disease Dataset
. -------------------------------------
. Competing Variables:
. -------------------------------------
. **Numeric** 
. age: age in years
. chol: serum cholestoral in mg/dl
. trestbps: resting blood pressure (in mm Hg on admission to the hospital)
. thalach: maximum heart rate achieved
. oldpeak : ST depression induced by exercise relative to rest
. **Categorical**
. sex: sex (1 = male; 0 = female)
. cp: chest pain type    
. fbs: (fasting blood sugar > 120 mg/dl)  (1 = true; 0 = false)
. restecg: resting electrocardiographic results
. exang: exercise induced angina (1 = yes; 0 = no)
. slope: the slope of the peak exercise ST segment
. ca: number of major vessels (0-3) colored by flourosopy
. thal: type of heart defect
. -------------------------------------
. Dependent Variable
. -------------------------------------
. target: diagnosis of heart disease (angiographic disease status)

Others Users Warning: change wd to read the datasets and after that to use the BAS package
```{r Loading the data dataset}
machine <- "server" # server, local
master_seed <- 1234

# getwd()
if (machine == "server") {
  setwd("/home/dbaptista")
} else if (machine == "local") {
  setwd("C:/Users/david/Downloads")
}

column_names <- c(
  "age", "sex", "cp", "trestbps", "chol", "fbs", "restecg",
  "thalach", "exang", "oldpeak", "slope", "ca", "thal", "target"
)

library(dplyr)
cleveland_heart <- read.table(
  "processed.cleveland.data",
  header = FALSE,
  col.names = column_names,
  sep = ",",
  na.strings  = "?") |> # Removing NA´s
  tidyr :: drop_na() |>
  mutate( # Converting variables into factors
    dplyr :: across(
      c(sex, cp, fbs, restecg, exang, slope, ca, thal, target),
      as.factor
    ),
    # y (target) = presence of heart disease in each patient
    target = factor(if_else(target == "0", "No", "Yes"))
  )

# Num of col of the corresponding overparameterized design matrix
p_over <- cleveland_heart |> 
  dplyr::select(-target) |> # Design Matrix
  dplyr::summarise(
    dplyr::across(
      dplyr::everything(),
      ~ if (is.factor(.x)) nlevels(.x) else 1L
    )) |>
  unlist() |>
  sum()
# print(p_over) # Unfeasible to enumerate
```

```{r Loading the costs dataset}
custos <- read.table(
  "all_costs_info",
  header = FALSE,
  sep = ",",
  col.names = c(
    "Variables", "Marginal Cost",
    "Discounted Cost", "Immediate", "Group"
  )) |>
  dplyr :: select(-4) |> # Remove Immediate column
  dplyr :: mutate(
    Group = recode(Group,
      "None" = 0,
      "A" = 1,
      "B" = 2,
      "C" = 3
    ))

if (machine == "server")
  setwd("/home/dbaptista/BAS")
```

```{r Building the mat (var.costs), basglm argument}
costs_mat <- matrix (1, nrow = nrow (custos), ncol = nrow (custos) + 1)
rownames (costs_mat) <- as.character (custos [, 1])
colnames (costs_mat) <- c ("Groups", rownames (costs_mat))

# Variables Groups...
costs_mat [, 1] <- as.numeric (custos [, 4])

# Marginal Costs
for (i in seq_len (nrow (costs_mat)))
  costs_mat [, i + 1] <- as.numeric (custos [i, 2]) 

old_costs_mat <- costs_mat
old_costs_mat [, 1] <- 0 # No costs structures

# Discounted Costs (single group)
costs_mat ["chol", "fbs"] <- 5.17
costs_mat ["fbs", "chol"] <- 3.10
# Grouped Predictors (2 groups)
costs_mat ["thal", "thalach"]  <- 1.0
costs_mat ["thalach", "thal"]  <- 1.0
#
costs_mat ["exang", "oldpeak"] <- 1.0
costs_mat ["exang", "slope"]   <- 1.0
costs_mat ["oldpeak", "exang"] <- 1.0
costs_mat ["oldpeak", "slope"] <- 1.0
costs_mat ["slope", "exang"]   <- 1.0
costs_mat ["slope", "oldpeak"] <- 1.0

# print(costs_mat) # colSums must be equal for (columns) elements of the same group, after we subset the columns and rows for each group
```

```{r Options}
base_mat <- matrix (1, nrow = nrow (custos), ncol = nrow (custos) + 1)
base_mat [, 1] <- 0
rownames (base_mat) <- as.character (custos [, 1])
colnames (base_mat) <- c ("Groups", rownames (costs_mat))

costs_list <- list(
  no_costs = base_mat,
  no_discount = old_costs_mat, 
  discounted = costs_mat
)

bp_heart <- list(
  unit_info = BAS::g.prior(g = nrow(cleveland_heart)) 
)
b_grid <- as.double(seq (from = 0, to = 0.6, by = 0.03))
```

```{r Column Names BAS and positions matrix}
library(AUC)

run_one_heart <- function(mp_name, bp_name, b_grid, costs_name = NULL, i) {

  if (mp_name == "FND_Const") {
    mp <- BAS:::FNDConst(b = b_grid[i])
  } else if (mp_name == "FND_SB") {
    mp <- BAS:::FNDSB(b = b_grid[i])
  }   

  # Initial Model:
  # Null Model: NULL
  # Random Model: c(1,rbinom(n = p_over, size = 1, prob = .5))
  # Full Model: rep(1, p_over + 1)
  init_model <- c(1, rbinom(n = p_over, size = 1, prob = .5))

  # system.time(
  obj <- BAS::bas.glmFC(
    formula = target ~ .,
    family = binomial(link = "logit"),
    data = cleveland_heart,
    betaprior = bp_heart[[bp_name]],
    modelprior = mp,
    var.costs = costs_list[[costs_name]],
    method = "GibbsBVS",
    bestmodel = init_model,
    burnin.iterations = 10000, # 10000
    MCMC.iterations = 100000, # 100000
    laplace = FALSE, # set to true for CCH and beta-prime
    renormalize = FALSE, # PIPs = MCMC relative frequencies of inclusion
    GROW = TRUE,
    expand = 1.25,
    n.models.init = 5000 # 10000
  )
  #)
  
  cat("b value: ", b_grid[i], "\n")

  # HPM
  # cat("HPM:", obj$HPM_short, "\n")  
  cat("Cost HPM:", obj$HPM_cost, "\n") 
  len_HPM <- length(obj$HPM_extended) # - 1 (no need I think...)
  cat("Length MPM:", len_HPM, "\n") 
  # In-Sample Predictions: newdata = cleveland_heart or NULL
  test_HPM = BAS:::predict.basglm (obj, newdata = NULL, type = "response",  estimator = "HPM")$fit;
  auc_hpm = auc(roc(test_HPM, cleveland_heart$target)); # AUC
  # cat("AUC HPM:", auc_hpm, "\n") 

  # MPM
  # cat("MPM:", obj$MPM_short, "\n") # Binary Indicator (competing variables): check also _extended
 
  cat("Cost MPM_dummy:", obj$MPM_extended_cost, "\n")  
  len_MPM_dummy <- sum(obj$MPM_extended > 0) - 1
  cat("Length MPM_dummy:", len_MPM_dummy, "\n") 

  len_MPM_grouped <- sum(obj$MPM_grouped > 0) - 1
  cat("Length MPM_grouped:", len_MPM_grouped, "\n") 
   cat("Cost MPM_grouped:", obj$MPM_grouped_cost, "\n")  

  # print ("MPM extended\n")
  # print(obj$MPM_extended)

  bas_MPM_dummy <- BAS::bas.glmFC(
    formula = target ~ .,
    family = binomial(link = "logit"),
    data = cleveland_heart,
    betaprior = bp_heart[[bp_name]],
    modelprior = mp,
    method = "GibbsBVS",
    bestmodel = obj$MPM_extended,
    burnin.iterations = 0, # 10000
    MCMC.iterations = 0, # 100000
    renormalize = FALSE, # PIPs = MCMC relative frequencies of inclusion
    GROW = TRUE,
    expand = 1,
    n.models.init = 1 
  )
  test_MPM_dummy = BAS:::predict.basglm (bas_MPM_dummy, newdata = NULL, type = "response",  estimator = "HPM")$fit;
  auc_mpm_dummy = auc(roc(test_MPM_dummy, cleveland_heart$target)); # AUC
  # cat("AUC MPM_dummy:", auc_mpm_dummy, "\n") 

  bas_MPM_grouped <- BAS::bas.glmFC(
    formula = target ~ .,
    family = binomial(link = "logit"),
    data = cleveland_heart,
    betaprior = bp_heart[[bp_name]],
    modelprior = mp,
    method = "GibbsBVS",
    bestmodel = obj$MPM_grouped,
    burnin.iterations = 0, # 10000
    MCMC.iterations = 0, # 100000
    renormalize = FALSE, # PIPs = MCMC relative frequencies of inclusion
    GROW = TRUE,
    expand = 1,
    n.models.init = 1 
  )
  test_MPM_grouped = BAS:::predict.basglm (bas_MPM_grouped, newdata = NULL, type = "response",  estimator = "HPM")$fit;
  auc_mpm_grouped = auc(roc(test_MPM_grouped, cleveland_heart$target)); # AUC
  # cat("AUC MPM_grouped:", auc_mpm_grouped, "\n") 

  send <- list (
    PIPs = obj$pip.MCMC,
    HPM_Cstat = auc_hpm,
    MPM_dummy_Cstat = auc_mpm_dummy,
    MPM_grouped_Cstat = auc_mpm_grouped,
    HPM_cost = obj$HPM_cost,
    MPM_dummy_cost = obj$MPM_extended_cost,
    MPM_grouped_cost = obj$MPM_grouped_cost
  )

}
```

## Table Object for LaTeX
```{r Cost table PDF}
predictor_labels <- c(
  age      = "age",
  sex      = "sex",
  cp       = "chest pain",
  trestbps = "resting BP",
  chol     = "cholesterol",
  fbs      = "blood sugar",
  restecg  = "EKG",
  thalach  = "heart rate",
  exang    = "exercise angina",
  oldpeak  = "ST depression",
  slope    = "peak ST segment",
  ca       = "major vessels",
  thal     = "defect type"
)

cost_table <- read.table(
  "all_costs_info",
  header = FALSE,
  sep = ",",
  col.names = c(
    "Variables", "Marginal.Cost",
    "Discounted.Cost", "Immediate", "Group"
  )
) |>
  dplyr::mutate(
    Label = predictor_labels[Variables],
    Discounted.Cost = ifelse(
      Group == "None", "--", sprintf("%.2f", Discounted.Cost)
    ),
    Marginal.Cost = sprintf("%.2f", Marginal.Cost),
    Group = ifelse(Group == "None", "--", Group)
  ) |>
  dplyr::select(Label, Marginal.Cost, Discounted.Cost, Group)

escape_tex <- function(x) gsub("&", "\\\\&", x)

tex_rows <- paste(
  apply(cost_table, 1, function(r) {
    paste(escape_tex(r["Label"]), r["Marginal.Cost"],
          r["Discounted.Cost"], r["Group"], sep = " & ")
  }),
  "\\\\"
)

tex_body <- paste(tex_rows, collapse = "\n")

tex_doc <- sprintf('
\\documentclass[11pt]{article}
\\usepackage[margin=1in]{geometry}
\\usepackage{booktabs}
\\usepackage{xcolor}
\\usepackage{array}
\\pagestyle{empty}

\\begin{document}
\\begin{table}[htbp]
\\centering
\\renewcommand{\\arraystretch}{1.3}
\\rowcolors{2}{gray!8}{white}
\\begin{tabular}{l r r c}
\\toprule
\\textbf{Variable} & \\textbf{Marginal Cost} & \\textbf{Discounted Cost} & \\textbf{Group} \\\\
\\midrule
%s
\\bottomrule
\\end{tabular}
\\caption{Marginal and discounted acquisition costs by predictor. Variables with no group discount are marked with \\textendash{}.}
\\end{table}
\\end{document}
', tex_body)

writeLines(tex_doc, "cost_table.tex")
```

```{bash Compile cost table PDF, engine.opts=""}
# cd "$(pwd 2>/dev/null || echo .)"
# pdflatex -interaction=nonstopmode cost_table.tex > cost_table_latex.log 2>&1
# echo "Exit status: $?"
# ls -la cost_table.pdf
``` 

## Fitting
```{r results function}
library (future.apply)

sim_results_heart <- function (b_grid, mp_name, bp_name, costs_name,
                                parallel = FALSE, workers = 2,
                                progress = TRUE, progress_file = NULL) {

  n_runs <- length (b_grid)

  if (!is.null (progress_file)) progress_file <- path.expand (progress_file)
  
  rss_mb <- function () {
    as.numeric (strsplit (readLines ("/proc/self/statm", n = 1L), " ")[[1L]][2L]) *
      4096 / 1024^2
  }

  say <- function (event, i, b, secs = NA_real_) {
    if (!progress) return (invisible (NULL))
    line <- sprintf (
      "[%s] pid %6d | %-5s %2d/%2d | b=%.2f | rss=%6.0f MB%s\n",
      format (Sys.time (), "%H:%M:%S"), Sys.getpid (), event, i, n_runs,
      b, rss_mb (),
      if (is.na (secs)) "" else sprintf (" | took %6.1f s", secs)
    )
    if (is.null (progress_file)) cat (line)
    else cat (line, file = progress_file, append = TRUE)
  }

  run_one <- function (i) {
    b_i <- b_grid [i]

    # Same seed on every iteration, deliberately: b and modelprior are the
    # only things we want to vary across runs
    set.seed (master_seed)

    say ("START", i, b_i)
    t0 <- Sys.time ()

    res <- run_one_heart (
      mp_name    = mp_name,
      bp_name    = bp_name,
      b_grid     = b_grid,
      costs_name = costs_name,
      i          = i
    )

    say ("DONE", i, b_i, as.numeric (difftime (Sys.time (), t0, units = "secs")))
    res
  }

  if (parallel) {
    # multisession, deliberately, not multicore: a fork inherits an already
    # multi-threaded BLAS, and workers end up fighting over cores.
    plan (multisession, workers = workers)
    on.exit (plan (sequential), add = TRUE)

    pip_list <- future_lapply (
      X = seq_along (b_grid),
      FUN = run_one,
      future.seed = FALSE
    )
    message ("sim_results_heart used: ", future::nbrOfWorkers (), " workers")
  } else {
    pip_list <- lapply (X = seq_along (b_grid), FUN = run_one)
  }

  pips_list              <- lapply (pip_list, `[[`, "PIPs")
  hpm_cost_list          <- lapply (pip_list, `[[`, "HPM_cost")
  mpm_dummy_cost_list    <- lapply (pip_list, `[[`, "MPM_dummy_cost")
  mpm_grouped_cost_list  <- lapply (pip_list, `[[`, "MPM_grouped_cost")
  hpm_cstat_list         <- lapply (pip_list, `[[`, "HPM_Cstat")
  mpm_dummy_cstat_list   <- lapply (pip_list, `[[`, "MPM_dummy_Cstat")
  mpm_grouped_cstat_list <- lapply (pip_list, `[[`, "MPM_grouped_Cstat")

  graph_pips <- do.call (rbind, pips_list)  # PIP´s at the level of variables only
  rownames (graph_pips) <- b_grid
  colnames (graph_pips) <- colnames(cleveland_heart)[1:13]

  hpm_cost <- setNames (unlist (hpm_cost_list), b_grid)
  mpm_dummy_cost <- setNames (unlist (mpm_dummy_cost_list), b_grid)
  mpm_grouped_cost <- setNames (unlist (mpm_grouped_cost_list), b_grid)

  hpm_cstat <- unlist (hpm_cstat_list)
  if (!is.null (hpm_cstat)) names (hpm_cstat) <- b_grid
  mpm_dummy_cstat <- unlist (mpm_dummy_cstat_list)
  if (!is.null (mpm_dummy_cstat)) names (mpm_dummy_cstat) <- b_grid
  mpm_grouped_cstat <- unlist (mpm_grouped_cstat_list)
  if (!is.null (mpm_grouped_cstat)) names (mpm_grouped_cstat) <- b_grid

  list (
    pips = graph_pips,
    hpm_cost = hpm_cost,
    mpm_dummy_cost = mpm_dummy_cost,
    mpm_grouped_cost = mpm_grouped_cost,
    hpm_cstat = hpm_cstat,
    mpm_dummy_cstat = mpm_dummy_cstat,
    mpm_grouped_cstat = mpm_grouped_cstat,
    mp_name = mp_name, costs_name = costs_name
  )
}
```

```{r Running the function}
results_FNDConst <- sim_results_heart (
  b_grid, "FND_Const", "unit_info", "no_discount", # "no_costs", "no_discount", "discounted"
  parallel = TRUE, workers = length(b_grid), progress = FALSE #, progress_file = "~/sim_heart.log"
)

results_FNDSB <- sim_results_heart (
  b_grid, "FND_SB", "unit_info", "no_discount", #  "no_costs", "no_discount", "discounted"
  parallel = TRUE, workers = length(b_grid), progress = FALSE #, progress_file = "~/sim_heart.log"
)
```

```{r Model cost plot function}
library (ggplot2)

plot_model_cost <- function (results, title = NULL) {

  b <- as.numeric (names (results$hpm_cost))

  df_cost <- data.frame (
    b = rep (b, 3),
    cost = c (results$hpm_cost, results$mpm_dummy_cost, results$mpm_grouped_cost),
    `Estimator` = rep (
      c ("HPM", "MPM (dummies)", "MPM (grouped)"),
      each = length (b)
    ),
    check.names = FALSE
  )

  ggplot (df_cost, aes (x = b, y = cost, colour = Estimator)) +
    geom_step (linewidth = 0.8) +
    scale_colour_manual (
      name = "Estimator",
      values = c (
        "HPM" = "black",
        "MPM (dummies)" = "red",
        "MPM (grouped)" = "blue"
      )
    ) +
    labs (
      title = title,
      x = "Cost Penalty Tuning Parameter 'b'",
      y = "(Real) Model Cost" # \n(per patient/observation)
    ) +
    ylim (0, 400) +
    theme_bw () +
    theme (
      legend.position = "right",
      plot.title = element_text (face = "bold"),
      axis.title.x = element_text (face = "bold"),
      axis.title.y = element_text (face = "bold"),
      legend.title = element_text (face = "bold")
    )
}
# plot_model_cost (results_FNDConst, "FND-Const")
# plot_model_cost (results_FNDSB, "FND-SB")
```

```{r Saving the model cost plots}
out_dir <- path.expand ("~/heart_experiments")
if (!dir.exists (out_dir)) dir.create (out_dir)

cost_graphs <- list (results_FNDConst, results_FNDSB)

for (res in cost_graphs) {

  p <- plot_model_cost (res, paste0 (res$mp_name, " (", res$costs_name, ")"))

  base_file <- file.path (
    out_dir, paste0 ("model_cost_", res$mp_name, "_", res$costs_name)
  )

  # ggsave (paste0 (base_file, ".png"), plot = p, width = 7, height = 5, dpi = 300)
  ggsave (paste0 (base_file, ".pdf"), plot = p, width = 7, height = 5)
}
```

```{r C-statistic plot function}
library (ggplot2)

plot_cstat <- function (results, title = NULL) {

  b <- as.numeric (names (results$hpm_cstat))

  df_cstat <- data.frame (
    b = rep (b, 3),
    cstat = c (results$hpm_cstat, results$mpm_dummy_cstat, results$mpm_grouped_cstat),
    `Estimator` = rep (
      c ("HPM", "MPM (dummies)", "MPM (grouped)"),
      each = length (b)
    ),
    check.names = FALSE
  )

  ggplot (df_cstat, aes (x = b, y = cstat, colour = Estimator)) +
    geom_step (linewidth = 0.8) +
    scale_colour_manual (
      name = "Estimator",
      values = c (
        "HPM" = "black",
        "MPM (dummies)" = "red",
        "MPM (grouped)" = "blue"
      )
    ) +
    labs (
      title = title,
      x = "Cost Penalty Tuning Parameter 'b'",
      y = "C-statistic"
    ) +
    scale_y_continuous (limits = c (0.75, 1), expand = c (0.01, 0.01)) +
    theme_bw () +
    theme (
      legend.position = "right",
      plot.title = element_text (face = "bold"),
      axis.title.x = element_text (face = "bold"),
      axis.title.y = element_text (face = "bold"),
      legend.title = element_text (face = "bold")
    )
}
# plot_cstat (results_FNDConst, "FND-Const")
# plot_cstat (results_FNDSB, "FND-SB")
```

```{r Saving the C-statistic plots}
cstat_graphs <- list (results_FNDConst, results_FNDSB)

for (res in cstat_graphs) {

  p <- plot_cstat (res, paste0 (res$mp_name, " (", res$costs_name, ")"))

  base_file <- file.path (
    out_dir, paste0 ("cstat_", res$mp_name, "_", res$costs_name)
  )

  # ggsave (paste0 (base_file, ".png"), plot = p, width = 7, height = 5, dpi = 300)
  ggsave (paste0 (base_file, ".pdf"), plot = p, width = 7, height = 5) # vector graphics: sharp at any print size in LaTeX
}
```

```{r Inclusion path plot function}
library (reshape2)   # melt()
library (ggplot2)
library (RColorBrewer)

# Same order as that of cleveland_heart / old_costs_mat.
predictor_labels <- c (
  age      = "age",
  sex      = "sex",
  cp       = "chest pain",
  trestbps = "resting BP",
  chol     = "cholesterol",
  fbs      = "blood sugar",
  restecg  = "EKG",
  thalach  = "heart rate",
  exang    = "exercise angina",
  oldpeak  = "ST depression",
  slope    = "peak ST segment",
  ca       = "major vessels",
  thal     = "defect type"
)

plot_inclusion_path <- function (results, title = "Inclusion Path produced by ECP") {

  marginal_cost <- diag (old_costs_mat [, -1])
  ord <- names (sort (marginal_cost, decreasing = FALSE))

  pips_ord <- results$pips [, ord, drop = FALSE]
  colnames (pips_ord) <- predictor_labels [ord]

  df_long <- melt (
    pips_ord,
    varnames = c ("b", "Predictor"),
    value.name = "PIP"
  )
  df_long$b <- as.numeric (as.character (df_long$b))  # melt() makes it factor
  df_long$Predictor <- factor (df_long$Predictor, levels = predictor_labels [ord])

  n_pred <- length (ord)
  cols <- colorRampPalette (brewer.pal (9, "Reds")) (n_pred)

  ggplot (df_long,
         aes (x = b, y = PIP,
              colour   = Predictor,
              linetype = Predictor,
              group    = Predictor)) +
    geom_line (linewidth = 1) +
    scale_colour_manual (values = cols) +
    scale_linetype_manual (values = rep_len (1:6, n_pred)) +
    scale_y_continuous (limits = c (0, 1), expand = c (0.01, 0.01)) +
    scale_x_continuous (expand = c (0, 0)) +
    labs (title = title,
          x = "Cost Penalty Tuning Parameter 'b'",
          y = "PIPs") +
    theme_minimal (base_size = 13) +
    theme (
      plot.title       = element_text (face = "bold", hjust = 0.5),
      axis.title.x     = element_text (face = "bold"),
      axis.title.y     = element_text (face = "bold"),
      legend.title     = element_text (face = "bold"),
      legend.key.width = unit (1.4, "cm")
    )
}
```

```{r Saving the inclusion path plots}
inclusion_graphs <- list (results_FNDConst, results_FNDSB)

for (res in inclusion_graphs) {

  p <- plot_inclusion_path (
    res, paste0 ("Inclusion Path (", res$mp_name, ", ", res$costs_name, ")")
  )

  base_file <- file.path (
    out_dir, paste0 ("inclusion_path_", res$mp_name, "_", res$costs_name)
  )

  # ggsave (paste0 (base_file, ".png"), plot = p, width = 9, height = 5, dpi = 300)
  ggsave (paste0 (base_file, ".pdf"), plot = p, width = 9, height = 5) # vector graphics: sharp at any print size in LaTeX
}
```

```{r Run Above}
# Run Above
```