---
title: "VSFactors - 1st Simul"
author: "David Baptista"
output: html_document
---

WARNING: computations were made using a HAL server. Local machine is only useful if smaller experiments are made or for your personal use
```{r Package Load/Install}
# -----------------------------------------
# Local Machine (directly from GitHub)
# -----------------------------------------
#remove.packages ("BAS", source = "CRAN")
#devtools::install_github (
#  "davidembb20/BAS",
#  ref = "costs_and_factors",
#  force = TRUE
#)
# -----------------------------------------
# HAL server
# -----------------------------------------
# e.g., download the package from GitHub to your local machine and then to the server, and set that folder as wd
#install.packages (".", repos = NULL, type = "source")
# -----------------------------------------

Sys.setenv(OMP_NUM_THREADS = "1", OPENBLAS_NUM_THREADS = "1") # Faster parallel computing
# to use with multisession, deliberately (not multicore), so that workers don´t end up fighting over cores.
library (BAS)
```

# 1st Experiment: VSFactors
What happens when increase the number of spurious factors are increased?
3 different scenarios are tested. For each, $n = 300$, and there are $p$ factors, all with the same number of levels, $l_j = 4$. Across all scenarios, there are only two active factors. The rest $p-2$ factors are spurious. Scenarios: $p \in \{ 5,15,27 \}$. Each experiment is repeated 10 times (which means there is a total of 30 simulated datasets, 10 per each value of $p$).
```{r Options}
lj <- 4 # Number of levels
n <- 300 # Sample size
alpha <- 1 # Intercept

intensity <- 0.50
beta1 <- c(-1.08, -.84, -.74, .63) * intensity
beta2 <- c(-0.51 * intensity, .41, .18, .07)

# Model Space Priors
mp <- list(
  CC   = BAS:::CC(),
  SBC  = BAS:::SBC(),
  SBSB = BAS:::SBSB()
)

metodo <- "GibbsBVS" # GibbsBVS, deterministic
machine <- "server" # server, local
master_seed <- 1234

num_p <- list(
  p5 = 5,
  p15 = 15,
  p27 = 27
)

num_iter <- 10

# Cartesian Product (df)
scenarios1 <- expand.grid(
  p_val = unlist(num_p),
  simulation_id  = seq_len(num_iter)
)
```

```{r Priors on Model Parameters}
priors_on_beta <- list(
  robust       = BAS::robust(n = n) #,
  # intrinsic    = BAS::intrinsic(n = n),
  # beta_prime   = BAS::beta.prime(n = n),
  # CH_a05_bn    = BAS::CCH(alpha = 1 / 2, beta = n),
  # CH_a1_bn     = BAS::CCH(alpha = 1, beta = n),
  # CH_a05_b05n  = BAS::CCH(alpha = 1 / 2, beta = n / 2),
  # CH_a1_b05n   = BAS::CCH(alpha = 1, beta = n / 2),
  # unit_inf_DBF = BAS::g.prior(g = n),
  # unit_inf_TBF = BAS::testBF.prior(g = n),
  # ZS_adapted   = BAS::CCH(alpha = 1, beta = 2, s = n + 3),
  # benchmark    = BAS::CCH(alpha = 0.02, beta = 0.02 * max(n, p^2)), # need to define p before this if used; with the recommended c = 0.01;
  # hyper_gn     = BAS::hyper.g.n(alpha = 3), # special case of the robust prior...
  # BIC          = BAS::bic.prior(n), # favors small models
	# AIC          = BAS::aic.prior(), # favours large models
  # local_eb     = BAS::EB.local() # tends to favor large models
)
```

```{r Simulated Data with Parallel}
library(future.apply)
library(dplyr)

# multisession, deliberately, not multicore: a fork inherits an already
# multi-threaded BLAS, and workers end up fighting over cores.
plan(multisession, workers = num_iter)

sim_list <- future_lapply(
  seq_len(num_iter), # 10 datasets
  function(j) {

    # Design matrix
    X <- matrix(
      sample(seq_len(lj), size = n * (25 + 2), replace = TRUE),
      nrow = n,
      ncol = (25 + 2) # Maximum number of competing factors
    )

    # Overparameterized design matriz
    X_over <- matrix(0, nrow = n, ncol = (25 + 2) * lj)

    # One-hot encoding
    for (k in seq_len(ncol(X))) {
      # Sequence of columns in X_over corresponding to the k-th column in X (k-th factor)
      # When lj = 4 => if k=1, cols = 1:4; if k=2, cols = 5:8, etc.
      # cols <- (k - 1) * lj + 1:lj
      # print (cols)

      # So, (k - 1) * lj + X[, k] gives the exact column index in X_over
      # where the "1" should go for each row 
           
      # cbind(1:n, ...) creates those (row, column) index pairs
      X_over[cbind(1:n, (k - 1) * lj + X[, k])] <- 1 # Other positions remain 0 
    }

    beta <- c(beta1[seq_len(lj)], beta2[seq_len(lj)], rep(0, 25 * lj))
    eta <- alpha + X_over %*% beta # Linear predictor
  
    y <- rpois (n, lambda = exp(eta)) # Poisson with log link
    # y <- rbinom(n, size = 1, prob = plogis(eta))
    # y <- rexp (n, rate = exp(eta)) # Exponential with log link

    sim_data <- as.data.frame(X) |>
      dplyr :: mutate(dplyr :: across(everything(), as.factor)) |> # character to factor 
      setNames(paste0("A", seq_len(ncol(X)))) |> # colNames
      mutate(y = y, .before = 1)
  
    sim_data

  },
  future.seed = master_seed # 1234
)

plan (sequential)
```

```{r Build Formulas}
# No need to include the intercept
build_formula <- function(p) {
  vars <- paste0("A", seq_len(p))
  formula <- as.formula(
    paste("y ~", paste(vars, collapse = " + "))
  )
  return(formula)
}
```

```{r Run bas_glmFC deterministic}
run_deterministic1 <- function(mp_name, sim_id, p = 2, bp_name) {
  
  obj <- BAS::bas.glmFC(
    formula = build_formula(p),
    family = poisson(link = "log"),
    data = sim_list[[sim_id]],
    betaprior = priors_on_beta [[bp_name]],
    modelprior = mp[[mp_name]],
    method = "deterministic",
    laplace = FALSE, # set to true for CCH and beta-prime
    store_less = TRUE
  )
  return (obj$pip)
}
```

```{r Run bas_glmFC GibbsBVS}
run_gibbs1 <- function(mp_name, sim_id, p = 2, bp_name) {

  cat("\nsim_id: ", sim_id, "\n")
  cat("num_p: ", p, "\n\n")

  # Initial Model:
  # NULL (default)
  # Random Model: c(1, rbinom(n = p * lj, size = 1, prob = .5))
  # Full Model: rep(1, (p*lj) + 1)
  init_model <- c(1, rbinom(n = p * lj, size = 1, prob = .5))

  obj <- BAS::bas.glmFC(
    formula = build_formula(p),
    family = poisson(link = "log"),
    data = sim_list[[sim_id]],
    # n.models = 10000,
    betaprior = priors_on_beta [[bp_name]],
    modelprior = mp[[mp_name]],
    method = "GibbsBVS", # Requires (p-1) marginal likelihood evaluations per iteration (with p referring to the overparameterized design matrix)
    bestmodel = init_model,
    burnin.iterations = 2000, # 10000
    MCMC.iterations = 20000, # 100000
    laplace = FALSE, # set to true for CCH and beta-prime
    renormalize = FALSE, # PIPs are the MCMC relative frequencies of inclusion
    GROW = TRUE,
    expand = 1.25,
    n.models.init = 2500 # 2500, 5000, 10000
  )

  obj$pip.MCMC
}
```

```{r Results function}
sim_results <- function (scenarios1, m_p, b_p, parallel = FALSE, workers = 2,
                         progress = TRUE, progress_file = NULL) {

  p_vals <- unlist(num_p)
  n_runs <- nrow(scenarios1)

  if (!is.null(progress_file)) progress_file <- path.expand(progress_file)

  # Auxiliary function to get the resident set size (RSS) in MB for the current R proces 
  rss_mb <- function () {
    as.numeric(strsplit(readLines("/proc/self/statm", n = 1L), " ")[[1L]][2L]) *
      4096 / 1024^2
  }

  # Auxiliary function to print progress messages
  say <- function (event, i, p, sim_id, secs = NA_real_) {
    if (!progress) return (invisible(NULL))
    line <- sprintf(
      "[%s] pid %6d | %-5s %2d/%2d | p=%2d sim=%2d | rss=%6.0f MB%s\n",
      format(Sys.time(), "%H:%M:%S"), Sys.getpid(), event, i, n_runs,
      p, sim_id, rss_mb(),
      if (is.na(secs)) "" else sprintf(" | took %6.1f s", secs)
    )
    if (is.null(progress_file)) cat(line)
    else cat(line, file = progress_file, append = TRUE)
  }

  run_one1 <- function(i) {
    p_i   <- scenarios1$p_val[i]
    sim_i <- scenarios1$simulation_id[i]

    say ("START", i, p_i, sim_i)
    t0 <- Sys.time()

    res <- if (metodo == "deterministic") {
      run_deterministic1 (
        mp_name = m_p, sim_id = sim_i, p = p_i, bp_name = b_p
      )
    } else if (metodo == "GibbsBVS") {
      run_gibbs1 (
        mp_name = m_p, sim_id = sim_i, p = p_i, bp_name = b_p
      )
    }

    say ("DONE", i, p_i, sim_i,
         as.numeric(difftime(Sys.time(), t0, units = "secs")))
    res
  }

  if (parallel) {
    # multisession, deliberately, not multicore: a fork inherits an already
    # multi-threaded BLAS, and workers end up fighting over cores.
    plan (multisession, workers = workers)
    on.exit(plan (sequential), add = TRUE)

    mat_all <- future_lapply (
      X = seq_len(nrow(scenarios1)),
      FUN = run_one1,
      future.seed = master_seed
    )

    message ("sim_results used: ", future::nbrOfWorkers(), " workers")
  } else {
    mat_all <- lapply (X = seq_len(nrow(scenarios1)), FUN = run_one1)
  }

  # One matrix per p: each row a simulation repetition, each column a factor.
  # The tiers are already in ascending p, and within a tier run_one1 returns in
  # scenarios1 row order, so this lines up with names(out) below.
  out <- lapply(p_vals, function(p)
    do.call(rbind, mat_all[scenarios1$p_val == p]))

  names(out) <- paste0 ("p_", p_vals)
  return(out)
  
}
```

```{r Results}
system.time({
  results_SBSB <- sim_results(
    scenarios1, "SBSB",
    "robust", # robust, unit_inf_DBF, unit_inf_TBF
    parallel = TRUE, workers = 15, progress = FALSE #, progress_file = "~/sim_progress.log"
  )
})
# print(results_SBSB)

system.time({
  results_SBC <- sim_results(
    scenarios1, "SBC",
    "robust", # robust, unit_inf_DBF, unit_inf_TBF
    parallel = TRUE, workers = 15, progress = FALSE #, progress_file = "~/sim_progress.log"
  )
})
# print(results_SBC)

system.time({
  results_CC <- sim_results(
    scenarios1, "CC",
    "robust", # robust, unit_inf_DBF, unit_inf_TBF
    parallel = TRUE, workers = 15, progress = FALSE #, progress_file = "~/sim_progress.log"
  ) 
})
# print(results_CC)
```

```{r Transformations}
pips_CC   <- results_CC   |> do.call(cbind, .)
pips_SBC  <- results_SBC  |> do.call(cbind, .)
pips_SBSB <- results_SBSB |> do.call(cbind, .)

pips_all <- rbind(pips_CC, pips_SBC, pips_SBSB) |>
  as.data.frame() |>
  setNames(paste0("pip(", colnames(.), ")")) |>
  as.matrix() |>
  round(digits = 2)
# print(pips_all)
```

Others User Warning: change *path* variable! 
```{r Saving PIPs}
if (machine == "server") {
  path <- "/home/dbaptista/Exp1_results/"
} else if (machine == "local") {
  path <- "C:/Users/david/Downloads/"
}

if (metodo == "GibbsBVS") {
  excel_file <- paste0(path, "pips_gibbs.xlsx")
} else if (metodo == "deterministic") {
  excel_file <- paste0(path, "pips_deterministic.xlsx")
}

library(openxlsx)
saving_pips <- function(pips, num_p, file) {

  if (file.exists(file)) {
    wb <- loadWorkbook(file)
  } else {
    wb <- createWorkbook()
  }

  sheet_name <- paste0("l", lj)
  if (sheet_name %in% names(wb)) {
    removeWorksheet(wb, sheet_name)
  }
  addWorksheet(wb, sheet_name)

  # if (!(sheet_name %in% names(wb))) {
  #   addWorksheet(wb, sheet_name)
  # }

  # To create a Blank Worksheet (if needed)
  # removeWorksheet(wb, sheet_name)
  # addWorksheet(wb, sheet_name)

  p_vals <- unlist (num_p)

  begin <- 1
  for (i in seq_along (p_vals)) {

    end <- begin + p_vals[i] - 1
    aux_mat_i <- pips [, begin:end]

    pips_int <- cbind ( 
      aux_mat_i [1:num_iter,],                 # CC
      aux_mat_i [(num_iter+1):(2*num_iter),],  # SBC
      aux_mat_i [(2*num_iter+1):(3*num_iter),] # SBSB
    ) # 10 x (p_v)als[i]*3) Matrix

    headers <- rep (c("CC", "SBC", "SBSB"), each = p_vals[i])
    pips_out <- rbind (headers, pips_int) # 11 rows + colnames
    colnames (pips_out) <- colnames (pips_int)
    
    writeData(
      wb, sheet_name,
      pips_out,
      startRow = 1 + ((12 + 2)*(i-1)), # +2 for spacing
      startCol = 1,
      rowNames = FALSE,
      colNames = TRUE
    )

    begin <- end + 1

  }

  saveWorkbook (wb, excel_file, overwrite = TRUE)

}
saving_pips(pips_all, num_p, excel_file)
```

```{r Auxiliary Functions}
signals <- function(mat) {
  # 1st two columns of the matrix = Two active factors
  mat <- mat[, 1:2]
}

spurious <- function(mat) {
  # Rest of the columns of the matrix 
  mat <- mat [, -(1:2), drop = FALSE]
}
```

## Analysis of results and plots
```{r Number of signals corresponding to spurious factors}
# If it increases with p, then it means that the model space prior is not controlling for multiplicity. 
wrong_signals <- function(num_p, results, m_p, file = NULL) {
  
  p_vals <- unlist(num_p)

  line <- paste0("\n\nNumber of signals corresponding to spurious factors (l=",lj,")\n")
  line <- paste0(line, m_p, ":\n")
  
    for (i in seq_along(p_vals)) {
      
      wrong <- results[[i]] |> 
        spurious() |> 
        (\(x) sum(x > 0.5)) # Across all datasets
  
      line <- paste0(line, "p=", p_vals[i], ": ", wrong, ";  ")
    }
  
  line <- paste0(line, "\n")
  cat(line) # Printing

  if (!is.null(file)) {
    cat(line, file = file, append = TRUE)
  }

}

if (metodo == "GibbsBVS") {
  txt_file <- paste0(path, "wrong_signals_gibbs.txt")
} else if (metodo == "deterministic") {
  txt_file <- paste0(path, "wrong_signals_deterministic.txt")
}

wrong_signals(num_p, results_CC, "CC", txt_file)
wrong_signals(num_p, results_SBC, "SBC", txt_file)
wrong_signals(num_p, results_SBSB, "SBSB", txt_file)
```

```{r Custom function plot}
custom_plot <- function (title, num_p, results) {
  
  p_vals <- unlist (num_p)
  n <- length (p_vals)
  
  plot (
    seq_len(n), # x-axis positions to be labelled next
    rep (NA, n), # y-values (NA for now, points added later)
    ylim = c(0, 1), # y-axis limits (0 to 1, with a reference line at 0.5)
    type = "n", # "n" = just set up axes (no points drawn yet)
    xlab = "",                  
    xaxt = "n", # "don´t" draw x-axis yet
    ylab = "PIPs",     
    main = title 
  )
  
  axis (
    side = 1, # x-axis
    at = seq_len(n), # positions 
    labels = paste0("p = ", p_vals)
  )
  
  # Horizontal reference line at y = 0.5 
  abline (h = .5, col = gray (0.6))
  
  for (i in seq_along (p_vals)) {
    
    mat  <- results [[paste0 ("p_", p_vals[i])]]
    sig  <- signals (mat)
    spur <- spurious (mat)
    
    # Signals 
    points (
      rep(i, # Position i (in the x-axis)
          length(sig)),
      sig, # y-values
      col = 3 # Green
    )

    # Spurious Factors
    points (
      rep(i, length(spur)),
      spur,
      col = 2 # Red
    )
    
  }
  
}
```

```{r Plotting}
# par (mfrow = c(1, 3))
# custom_plot ("Const-Const", num_p, results_CC)
# custom_plot ("SB-Const", num_p, results_SBC)
# custom_plot ("SB-SB", num_p, results_SBSB)
```

```{r .pdf files with the graphs}
suffix <- if (metodo == "GibbsBVS") "_gibbs" else "_deterministic"

graphs <- list(
  CC   = list(title = "Const-Const", results = results_CC),
  SBC  = list(title = "SB-Const",    results = results_SBC),
  SBSB = list(title = "SB-SB",       results = results_SBSB)
)

for (mp_name in names(graphs)) {

  pdf_file <- paste0(path, "graphs_l", lj, suffix, "_", mp_name, ".pdf")

  pdf(pdf_file, width = 4, height = 7) # vector graphics: sharp at any print size in LaTeX
  custom_plot(graphs[[mp_name]]$title, num_p, graphs[[mp_name]]$results)
  dev.off()

}
```

```{r Run Above}
```

